---
title: "Cohort Comparison - Cohort Preparation"
author: "Jan Karregat"
date: "19.10.2023"
output: github_document
bibliography: index.bib
---

Based on Muriel Lobier's original code (https://github.com/FRCBS/iron_levels_of_blood_donors/blob/master/src/index.Rmd)

# Summary

This document includes all codes necessary to run the analysis of and produce the figures for the 5 Dutch Cohorts (DISIII, PREVEND, NEW Donors, and Helius). The code allows the user to describe the cohorts and build a summary table that can be used in further regression analysis.

```{r setup, , message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
library(haven)
library(foreign)
library(tidyverse)
library(tableone)
library(stargazer)
library(gridExtra)
library(cowplot)
library(broom)
library(GGally)
library(ggfortify)
library(knitr)
library(lubridate)
library(car)
library(sfsmisc)
library(MASS)
library(ordinal)
library(sjmisc)
library(epiDisplay)
#library(safeBinaryRegression)
library(epitools)
library(ez)
library(ggbeeswarm)
#install.packages("tidymodels")
#library(tidymodels)
library(ggthemes)
library(rsample)
library(broom)
library(scales)
library(kableExtra)
library(boot)
library(readxl)
library(tidylog, warn.conflicts = F)
```

## Data loading
We have two cohorts with blood donors, DIS III and NEW Donors, and three general population cohorts, PREVEND, HELIUS

```{r , warning=FALSE}
# Load DIS III data 
DataDis <- read.spss(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/1. Preparation [SPSS]/2. Datasets/1. Cohort Comparison - DIS III - Dataset.sav", to.data.frame=T)

# Load NEW Donor data
DataNEW <- read.spss(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/1. Preparation [SPSS]/2. Datasets/3. Cohort Comparison - NEW Donors - Dataset.sav", to.data.frame=T)

# Load PREVEND data
DataPrev <- read.spss(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/1. Preparation [SPSS]/2. Datasets/2. Cohort Comparison - PREVEND - Dataset.sav", to.data.frame=T)

# Load HELIUS data
DataHELIUS <- read.spss(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/1. Preparation [SPSS]/2. Datasets/5. Cohort Comparison - HELIUS - Dataset.sav", to.data.frame=T)
```

## Data preparation
First we assign study participants to their cohorts.
```{r}
# Create Cohort variable
DataDis$Cohort <- c("DISIII")
DataPrev$Cohort <- c("PREVEND")
DataNEW$Cohort <- c("NEW")
DataHELIUS$Cohort <- c("HELIUS")

# Adjust Hb (g/dL) and create empty Menstruation variable for NEW
DataDis$Hb <- DataDis$Hb/16.113
DataDis$Hb <- DataDis$Hb*1.6113
DataNEW$Hb <- DataNEW$Hb*1.6113
DataPrev$Hb <- DataPrev$Hb*1.6113
names(DataHELIUS)[names(DataHELIUS) == "H2_Lab_UitslagHEMO"] <- "Hb"
DataHELIUS$Hb <- as.numeric(as.character(DataHELIUS$Hb))
DataHELIUS$Hb <- DataHELIUS$Hb*1.6113

# Filter for whole blood donors or donors with at least 1 whole blood donation in last 2 years
DataDis <- DataDis %>% filter(DonorType_PriorDIS == "V" | FreqDonatie2Jaar > 0)

# Random sample from NEW Donors while dataset is disproportional big
DataNEW <- DataNEW %>% sample_frac(0.10)

# Determine number of unique cases
DataDis %>% distinct(KeyID) %>% nrow()
DataPrev %>% distinct(PK) %>% nrow()
DataNEW %>% distinct(ID) %>% nrow()
DataHELIUS %>% distinct(ID) %>% nrow()
```

## We adjust variable names and add blood volume to all cohorts
```{R}
# DIS
names(DataDis)[names(DataDis) == "KeyID"] <- "ID"
DataDis$Sex <- gsub("(?i)\\bFemale\\b", "Women", DataDis$Sex)
DataDis$Sex <- gsub("(?i)\\bMale\\b", "Men", DataDis$Sex)
names(DataDis)[names(DataDis) == "DagenLaatsteDonatie"] <- "DaysToPreviousFB"       # Whole blood donation
names(DataDis)[names(DataDis) == "FreqDonatie2Jaar"] <- "Donation_Freq_2YearsPrior" # Whole blood donations
DataDis <- DataDis %>% mutate(Donation_Freq_2YearsPrior = (ifelse(is.na(Donation_Freq_2YearsPrior), 0, Donation_Freq_2YearsPrior)))
DataDis$Smoking <- gsub("Nee, nooit", "No", DataDis$Smoking)
DataDis$Smoking <- gsub("Nee, maar wel gerookt", "No", DataDis$Smoking)
DataDis$Smoking <- gsub("Ja", "Yes", DataDis$Smoking)
DataDis$Smoking <- as.factor(DataDis$Smoking)
DataDis$Pregnancy <- gsub("Ja", "Yes", DataDis$Pregnancy)
DataDis$Pregnancy <- gsub("Nee", "No", DataDis$Pregnancy)
DataDis$Pregnancy <- as.factor(DataDis$Pregnancy)
names(DataDis)[names(DataDis) == "OCC_Pill"] <- "CurrentOCC"
DataDis$CurrentOCC <- gsub("Ja, ooit", "No", DataDis$CurrentOCC)
DataDis$CurrentOCC <- gsub("Ja, nu", "Yes", DataDis$CurrentOCC)
DataDis <- DataDis %>% mutate(CurrentOCC = (ifelse(Contraception == "Nee", "No", CurrentOCC)))
DataDis$CurrentOCC <- as.factor(DataDis$CurrentOCC)

# PREVEND
names(DataPrev)[names(DataPrev) == "PK"] <- "ID"
DataPrev$Sex <- gsub("(?i)\\bfemale\\b", "Women", DataPrev$Sex)
DataPrev$Sex <- gsub("(?i)\\bmale\\b", "Men", DataPrev$Sex)
DataPrev$Smoking <- gsub("Yes, still", "Yes", DataPrev$Smoking)
DataPrev$Smoking <- gsub("Yes, stopped > 1 year", "No", DataPrev$Smoking)
DataPrev$Smoking <- gsub("Yes, stopped < 1year", "No", DataPrev$Smoking)
DataPrev$Smoking <- gsub("No", "No", DataPrev$Smoking)
DataPrev$Smoking <- as.factor(DataPrev$Smoking)
DataPrev$CurrentOCC <- as.factor(DataPrev$CurrentOCC)

# NEW
DataNEW$Sex <- gsub("\\bM\\b", "Men", DataNEW$Sex)
DataNEW$Sex <- gsub("\\bF\\b", "Women", DataNEW$Sex)
DataNEW$Menstruation <- NA


# HELIUS
names(DataHELIUS)[names(DataHELIUS) == "H1_geslacht"] <- "Sex"
DataHELIUS$Sex <- gsub("vrouw", "Women", DataHELIUS$Sex)
DataHELIUS$Sex <- gsub("man", "Men", DataHELIUS$Sex)
names(DataHELIUS)[names(DataHELIUS) == "H1_lft"] <- "Age"
names(DataHELIUS)[names(DataHELIUS) == "H1_LftMenstrWeg"] <- "Menopause_Age"
DataHELIUS$Menopause_Age <- as.numeric(as.character(DataHELIUS$Menopause_Age))
names(DataHELIUS)[names(DataHELIUS) == "H1_MenstrNu"] <- "Menstruation"
DataHELIUS$Menstruation <- gsub("Ja", "Yes", DataHELIUS$Menstruation)
DataHELIUS$Menstruation <- gsub("Nee", "No", DataHELIUS$Menstruation)
names(DataHELIUS)[names(DataHELIUS) == "H1_Bevallen"] <- "Pregnancy"
DataHELIUS$Pregnancy <- gsub("Ja", "Yes", DataHELIUS$Pregnancy)
DataHELIUS$Pregnancy <- gsub("Nee", "No", DataHELIUS$Pregnancy)
names(DataHELIUS)[names(DataHELIUS) == "H1_VegaHoeveel"] <- "NoMeat_DaysPerWeek"
DataHELIUS$NoMeat_DaysPerWeek <- gsub("Nooit", "0", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("Minder dan 1 dag per week", "<1", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("1 dag per week", "1", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("2 dagen per week", "2", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("3 dagen per week", "3", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("4 dagen per week", "4", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("5 dagen per week", "5", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("6 dagen per week", "6", DataHELIUS$NoMeat_DaysPerWeek)
DataHELIUS$NoMeat_DaysPerWeek <- gsub("7 dagen per week", "7", DataHELIUS$NoMeat_DaysPerWeek)
names(DataHELIUS)[names(DataHELIUS) == "H2_Roken_H1combined"] <- "Smoking"
DataHELIUS$Smoking <- gsub("Nee, nooit gerookt", "No", DataHELIUS$Smoking)
DataHELIUS$Smoking <- gsub("Nee, maar vroeger wel", "No", DataHELIUS$Smoking)
DataHELIUS$Smoking <- gsub("Ja", "Yes", DataHELIUS$Smoking)
names(DataHELIUS)[names(DataHELIUS) == "H2_LO_GemGewicht"] <- "Weight"
DataHELIUS$Weight <- as.numeric(as.character(DataHELIUS$Weight))
names(DataHELIUS)[names(DataHELIUS) == "H2_LO_GemLengte"] <- "Length"
DataHELIUS$Length <- as.numeric(as.character(DataHELIUS$Length))
DataHELIUS$Length <- DataHELIUS$Length/100 # Length in meters
names(DataHELIUS)[names(DataHELIUS) == "H2_LO_BMI"] <- "BMI"
DataHELIUS$BMI <- as.numeric(as.character(DataHELIUS$BMI))
names(DataHELIUS)[names(DataHELIUS) == "H2_DM_Self_H1combined"] <- "Diabetes"
names(DataHELIUS)[names(DataHELIUS) == "H2_Lab_UitslagEFER"] <- "Ferritin"
DataHELIUS$Ferritin <- as.numeric(as.character(DataHELIUS$Ferritin))
names(DataHELIUS)[names(DataHELIUS) == "H2_Lab_UitslagCRPR"] <- "CRP"
DataHELIUS$CRP <- as.numeric(as.character(DataHELIUS$CRP))
names(DataHELIUS)[names(DataHELIUS) == "H1_Anticon2"] <- "CurrentOCC"
DataHELIUS$CurrentOCC <- gsub("Ja", "Yes", DataHELIUS$CurrentOCC)
DataHELIUS$CurrentOCC <- gsub("Niet geselecteerd", "No", DataHELIUS$CurrentOCC)
DataHELIUS$CurrentOCC <- as.factor(DataHELIUS$CurrentOCC)

```

# Blood Volume
```{r}
# Creat blood volum variable (Nadler’s equation)
calculate_blood_volume <- function(data) {
  data$blood_volume <- ifelse(data$Sex == "Women", (0.3561*data$Length^3) + (0.03308*data$Weight) + 0.1833, NA)
  data$blood_volume <- ifelse(data$Sex == "Men", (0.3669*data$Length^3) + (0.03219*data$Weight) + 0.6041, data$blood_volume)
  return(data)
}

# Use for all dataset
DataDis <- calculate_blood_volume(DataDis)
DataPrev <- calculate_blood_volume(DataPrev)
DataNEW <- calculate_blood_volume(DataNEW)
DataHELIUS <- calculate_blood_volume(DataHELIUS)
```

There are "cohort_name %>% distinct(ID_variable) %>% nrow()" individials enrolled in the studies. 


  * DIS III:   `r DataDis %>% distinct(KeyID) %>% nrow()`
  * PREVEND:   `r DataPrev %>% distinct(PK) %>% nrow()`
  * PREVEND:   `r DataNEW %>% distinct(ID) %>% nrow()`
        
Once we remove participants that have no ferritin or no Hb measurement data (and for blood donors for any donation event) there are `r cohort_name %>%  filter(!is.na(Ferritin) & !is.na(Hb_v) ) %>% distinct(ID_variable) %>% nrow()` participants left  

  * DIS III:    `r DataDis %>%  filter(!is.na(Ferritin) & !is.na(Hb) )                     %>% distinct(KeyID) %>% nrow()`
  * PREVEND:    `r DataPrev %>%  filter(!is.na(Ferritin) & !is.na(Hb) )                     %>% distinct(PK) %>% nrow()`

```{r , warning=FALSE}
DataDis %>%  filter(!is.na(Ferritin) & !is.na(Hb) ) %>% distinct(ID) %>% nrow()
DataPrev %>%  filter(!is.na(Ferritin) & !is.na(Hb) ) %>% distinct(ID) %>% nrow()
DataNEW %>%  filter(!is.na(Ferritin) & !is.na(Hb) ) %>% distinct(ID) %>% nrow()
DataHELIUS %>%  filter(!is.na(Ferritin) & !is.na(Hb) ) %>% distinct(ID) %>% nrow()
```
# Create datasets with variables of interest
Get values for first study donation with the required measurements donation (regardless of donation type)
We remove events with no Ferritin and Hb to be in line with the nb of previous donations were counted.
```{r , warning=FALSE}
#                           DIS III
DataDis_Summary <- DataDis %>% 
  group_by(ID) %>% 
  summarise(Sex=first(Sex)) 

DIS_data_summary <- DataDis %>%  
  dplyr::select(ID, Age, Sex, Ferritin, Hb, Cohort, Weight, BMI, Menstruation, CurrentOCC, Smoking, DaysToPreviousFB, Donation_Freq_2YearsPrior, TotalDonationPriorDIS, Alcohol, Diet, TotalIron, HemeIron, NonHemeIron, Pregnancy, blood_volume, Donation5YearPriorDIS) %>% 
  ungroup()

DIS_data_summary %>% distinct(ID) %>% nrow()


# NEW
DataNEW_Summary <- DataNEW %>% 
  group_by(ID) %>% 
  summarise(Sex=first(Sex)) 

NEW_data_summary <- DataNEW %>%  
  dplyr::select(ID, Age, Cohort, Sex, Ferritin, Hb, Weight, Length, BMI, Menstruation, blood_volume) %>% 
  ungroup()


# PREVEND 
PREV_data_summary <- DataPrev %>% 
  group_by(ID) %>% 
  summarise(Sex=first(Sex)) 

PREV_data_summary <- DataPrev %>%
  group_by(ID) %>%
  dplyr::select(ID, Age, Sex, Cohort, Ferritin, Hb, Weight, BMI, Menstruation, Smoking, CurrentOCC, CurrentOCCForContraception, Pregnancy, UlcurTreatment, blood_volume) %>%
  ungroup()

PREV_data_summary %>% distinct(ID) %>% nrow()


#                           HELIUS
HELIUS_data_summary <- DataHELIUS %>% 
  group_by(ID) %>% 
  summarise(Sex=first(Sex)) 
  
HELIUS_data_summary <- DataHELIUS %>%
  group_by(ID) %>%
  dplyr::select(ID, Age, Sex, Cohort, Ferritin, Hb, Weight, BMI, Menstruation, Menopause_Age, Smoking, CRP, blood_volume, Pregnancy, CurrentOCC, NoMeat_DaysPerWeek, Diabetes) %>%
  ungroup()
```



## Demographic group specification and assignment 

In this section we assign women to period/no period groups. The menstruation question was similar in three cohorts (DIS, PREVEND, New Donors). However no menstruation data is available for the NEW donors:

There are `r cohort_summary_name %>% filter(Sex == "Women" & is.na(Menstruation)) %>%  nrow()` women with no  answer to the question regarding their menstrual status. 

  * DISIII:   `r DIS_data_summary %>% filter(Sex == "Women" & is.na(Menstruation)) %>%  nrow()`
  * NEW:      `r NEW_data_summary %>% filter(Sex == "Women" & is.na(Menstruation)) %>%  nrow()`
  * PREVEND:  `r PREV_data_summary %>% filter(Sex == "Women" & is.na(Menstruation)) %>%  nrow()`

# Menopausal status: DIS
```{r}
# Create Menopause variable
DIS_data_summary <- DIS_data_summary %>% 
  mutate(Menopause = case_when(
   (Age > 50) ~ "postmenopausal",
   (Age <= 50) ~ "premenopausal"
    ))

```

# Menopausal status: PREVEND
```{r}
# Create Menopause variable
PREV_data_summary <- PREV_data_summary %>% 
  mutate(Menopause = case_when(
   (Age > 50) ~ "postmenopausal",
   (Age <= 50) ~ "premenopausal"
    ))

PREV_data_summary$Menopause <- as.factor(PREV_data_summary$Menopause)
```

# Menopausal status: NEW [only based on age]
```{r}
# Create Menopause variable
 NEW_data_summary <- NEW_data_summary %>%
  mutate(Menopause = case_when(
   (Age > 50) ~ "postmenopausal",
   (Age <= 50) ~ "premenopausal"
    ))

NEW_data_summary$Menopause <- as.factor(NEW_data_summary$Menopause)
```


# Menopausal status: HELIUS
```{r}
# Create Menopause variable
 HELIUS_data_summary <- HELIUS_data_summary %>% 
  mutate(Menopause = case_when(
   (Age > 50) ~ "postmenopausal",
   (Age <= 50) ~ "premenopausal"
    ))

HELIUS_data_summary$Menopause <- as.factor(HELIUS_data_summary$Menopause)

```

# Menstruation DIS
```{r}
# Remove pregnant women
names(DIS_data_summary)[names(DIS_data_summary) == "Menstruation"] <- "MenstruationFULL"
DIS_data_summary <- DIS_data_summary %>% filter(MenstruationFULL != "Nee, ik ben zwanger (geweest)" | is.na(MenstruationFULL))

#Adjust Menstruation to dichotomous variable
DIS_data_summary <- DIS_data_summary %>% 
  mutate(Menstruation = case_when(
    MenstruationFULL == "Nee, vanwege overgang" ~ "No", # women who report menopause to postmenopausal group
    MenstruationFULL == "Ja" ~ "Yes", # women who report menstruation to premenopausal group
    MenstruationFULL == "Nee, om een andere reden" ~ "No", # women >= 45 with no menstruation due to other reason to postmenopausal group
    Sex == "Men" ~ NA, # Men
   )) 


table(DIS_data_summary$Menopause,DIS_data_summary$Menstruation)

```

# Menstruation: PREVEND
```{r}
#Adjust Menstruation to dichotomous variable
names(PREV_data_summary)[names(PREV_data_summary) == "Menstruation"] <- "MenstruationFULL"
 PREV_data_summary <- PREV_data_summary %>% 
  mutate(Menstruation = case_when(
    MenstruationFULL == "Yes" ~ "Yes", 
    MenstruationFULL == "No, not anymore" ~ "No"
    ))

 table(PREV_data_summary$Menopause,PREV_data_summary$Menstruation)

```

# Menstruation: HELIUS
```{r}
# Menstruation is already dichotomous
# HELIUS_data_summary$Menopause <- as.factor(HELIUS_data_summary$Menopause)

# Determine NA's Menstruation
# HELIUS_data_summary %>%
#   filter(Sex == "Women" & is.na(Menstruation)) %>%
#   summarize(count = n())
```


# Create Group variable [Men, Pre- and Postmenopausal Women]
```{r}
# DIS
DIS_data_summary_final <- DIS_data_summary %>% 
  mutate(Group = case_when(
    Sex == "Men" ~ "Men", 
    Sex == "Women" & (Menopause == "postmenopausal") ~ "Women_Postmenopausal",
    Sex == "Women" & (Menopause == "premenopausal") ~ "Women_Premenopausal",
    TRUE ~ "NA")) %>% 
  mutate(Group = ordered(Group, levels =  c("Women_Premenopausal", "Women_Postmenopausal", "Men"))) 

# NEW
NEW_data_summary_final <- NEW_data_summary %>% 
  mutate(Group = case_when(
    Sex == "Women" & (Menopause == "postmenopausal") ~ "Women_Postmenopausal",
    Sex == "Women" & (Menopause == "premenopausal") ~ "Women_Premenopausal",
    Sex == "Men"  ~ "Men",
    TRUE ~ "NA")) %>%
    group_by(Group) %>% 
  # filter(Group != "Women_pre_menop_no_mens" & Group != "NA") %>%   # droplevels() %>% 
  mutate(Group = ordered(Group, levels =  c("Women_Premenopausal", "Women_Postmenopausal", "Men"))) 

# PREVEND
PREV_summary_final <- PREV_data_summary %>% 
  mutate(Group = case_when(
    Sex == "Men" ~ "Men", 
    Sex == "Women" & (Menopause == "postmenopausal") ~ "Women_Postmenopausal",
    Sex == "Women" & (Menopause == "premenopausal") ~ "Women_Premenopausal",
      TRUE ~ "NA")) %>% 
  droplevels() %>% 
  mutate(Group = ordered(Group, levels =  c("Women_Premenopausal", "Women_Postmenopausal", "Men"))) 

#  HELIUS
HELIUS_summary_final <- HELIUS_data_summary %>% 
  mutate(Group = case_when(
    Sex == "Women" & (Menopause == "postmenopausal") ~ "Women_Postmenopausal",
    Sex == "Women" & (Menopause == "premenopausal") ~ "Women_Premenopausal",
    Sex == "Men"  ~ "Men",
    TRUE ~ "NA")) %>%
    group_by(Group) %>% 
  # filter(Group != "Women_pre_menop_no_mens" & Group != "NA") %>%   # droplevels() %>% 
  mutate(Group = ordered(Group, levels =  c("Women_Premenopausal", "Women_Postmenopausal", "Men"))) 

```

# Align dataset for merge [add missing variables per cohort]
```{r}
# PREVEND
PREV_summary_final$Donation_Freq_2YearsPrior <- 0
PREV_summary_final$DaysToPreviousFB <- 0
PREV_summary_final$Alcohol <- NA
PREV_summary_final$Diet <- NA
PREV_summary_final$TotalIron <- NA
PREV_summary_final$HemeIron <- NA
PREV_summary_final$NonHemeIron <- NA
PREV_summary_final$CRP <- NA

# DIS
DIS_data_summary_final$CurrentOCCForContraception <- NA
DIS_data_summary_final$CurrentOCCForclimacterium <- NA
DIS_data_summary_final$UlcurTreatment <- NA
DIS_data_summary_final$IronSupplementation <- NA
DIS_data_summary_final$CRP <- NA

# NEW
NEW_data_summary_final$Donation_Freq_2YearsPrior <- 0
NEW_data_summary_final$DaysToPreviousFB <- 0
NEW_data_summary_final$Alcohol <- NA
NEW_data_summary_final$Diet <- NA
NEW_data_summary_final$TotalIron <- NA
NEW_data_summary_final$HemeIron <- NA
NEW_data_summary_final$NonHemeIron <- NA
NEW_data_summary_final$CurrentOCC <- NA
NEW_data_summary_final$CurrentOCCForContraception <- NA
NEW_data_summary_final$CurrentOCCForclimacterium <- NA
NEW_data_summary_final$UlcurTreatment <- NA
NEW_data_summary_final$IronSupplementation <- NA
NEW_data_summary_final$CRP <- NA
NEW_data_summary_final$Smoking <- NA
NEW_data_summary_final$Pregnancy <- NA

# HELIUS
HELIUS_summary_final$Donation_Freq_2YearsPrior <- 0
HELIUS_summary_final$DaysToPreviousFB <- 0
HELIUS_summary_final$Alcohol <- NA
HELIUS_summary_final$Diet <- NA
HELIUS_summary_final$TotalIron <- NA
HELIUS_summary_final$HemeIron <- NA
HELIUS_summary_final$NonHemeIron <- NA
HELIUS_summary_final$CurrentOCCForContraception <- NA
HELIUS_summary_final$CurrentOCCForclimacterium <- NA
HELIUS_summary_final$UlcurTreatment <- NA
HELIUS_summary_final$IronSupplementation <- NA

```

# Donation interval General Population Cohorts and DIS missings
```{r}
PREV_summary_final <- PREV_summary_final %>% mutate(DaysToPreviousFB = round(runif(nrow(PREV_summary_final), min = 3*365, max = 6*365) ,0))

NEW_data_summary_final <- NEW_data_summary_final %>% ungroup() %>% mutate(DaysToPreviousFB = round(runif(nrow(NEW_data_summary_final), min = 3*365, max = 6*365) ,0))

HELIUS_summary_final <- HELIUS_summary_final %>% ungroup() %>% mutate(DaysToPreviousFB = round(runif(nrow(HELIUS_summary_final), min = 3*365, max = 6*365) ,0))

# Add for DIS donors without donation in last 2 years
# DIS_data_summary_final <- DIS_data_summary_final %>% 
#   ungroup() %>% 
#   mutate(DaysToPreviousFB = ifelse(is.na(DaysToPreviousFB), 
#     round(runif(n(), min = 3 * 365, max = 6 * 365), 0), 
#     DaysToPreviousFB)
#     )

```

## Remove cohort participants with missing data ##

# Ferritin
```{r}
##DIS
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(Ferritin))

##PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(Ferritin))

##NEW
NEW_data_summary_final <- NEW_data_summary_final %>% 
  filter(!is.na(Ferritin))
  
##HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(Ferritin))
```

# Sex
```{r}
##DIS
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(Sex))

##PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(Sex))

##NEW
NEW_data_summary_final <- NEW_data_summary_final %>% 
  filter(!is.na(Sex))
  
##HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(Sex))
```
# Age
```{r}
#### DISIII
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(Age))

#### NEW
NEW_data_summary_final <- NEW_data_summary_final %>% 
  filter(!is.na(Age))

#### PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(Age))
  
#### HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(Age))
```
# Blood volume
```{r}
##DIS
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(blood_volume))

##PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(blood_volume))

##NEW
NEW_data_summary_final <- NEW_data_summary_final %>% 
  filter(!is.na(blood_volume))
  
##HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(blood_volume))
```
# Smoking
```{r}
#### DISIII
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(Smoking))

#### PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(Smoking))

### HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(Smoking))
```


# Menstruation
```{r}
#### DISIII
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(Menstruation) | Group == "Men")

#### PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(Menstruation) | Group == "Men")

### HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(Menstruation) | Group == "Men")
```
# Childbirth
```{r}
#### DISIII
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(Pregnancy) | Group == "Men")

#### PREVEND (3 men filled out the pregnancy question: changed to NA)
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(Pregnancy) | Group == "Men")

PREV_summary_final <- PREV_summary_final %>% 
  mutate(Pregnancy = ifelse(Group == "Men", NA, Pregnancy)) %>%
  mutate(Pregnancy = factor(Pregnancy))
PREV_summary_final$Pregnancy <- gsub(2, "Yes", PREV_summary_final$Pregnancy)
PREV_summary_final$Pregnancy <- gsub(1, "No", PREV_summary_final$Pregnancy)
PREV_summary_final$Pregnancy <- as.factor(PREV_summary_final$Pregnancy)

### HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(Pregnancy) | Group == "Men")
```
# Oral Contraception
```{r}
#### DISIII
DIS_data_summary_final <- DIS_data_summary_final %>% 
  filter(!is.na(CurrentOCC) | Group == "Men")

#### PREVEND
PREV_summary_final <- PREV_summary_final %>% 
  filter(!is.na(CurrentOCC) | Group == "Men")

### HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  filter(!is.na(CurrentOCC) | Group == "Men")
```


# Exclude extreme values [BMI and Weight]
```{r}
# DIS
DIS_data_summary_final <- DIS_data_summary_final %>% filter(BMI < 50)
DIS_data_summary_final <- DIS_data_summary_final %>% filter(Weight >= 50)

# PREVEND
PREV_summary_final <- PREV_summary_final %>% filter(BMI < 50)
PREV_summary_final <- PREV_summary_final %>% filter(Weight >= 50)

# NEW
NEW_data_summary_final <- NEW_data_summary_final %>% filter(BMI < 50)
NEW_data_summary_final <- NEW_data_summary_final %>% filter(Weight >= 50)

# HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% filter(BMI < 50)
HELIUS_summary_final <- HELIUS_summary_final %>% filter(Weight >= 50)
```
# Ferritin > 0
```{r}
DIS_data_summary_final <- DIS_data_summary_final %>%  filter(Ferritin > 0)
DIS_data_summary_final <- DIS_data_summary_final %>% filter(Ferritin < 400)

PREV_summary_final <- PREV_summary_final %>%  filter(Ferritin > 0)
PREV_summary_final <- PREV_summary_final %>% filter(Ferritin < 400)

NEW_data_summary_final <- NEW_data_summary_final %>% filter(Ferritin > 0)
NEW_data_summary_final <- NEW_data_summary_final %>% filter(Ferritin < 400)

HELIUS_summary_final <- HELIUS_summary_final %>% filter(Ferritin > 0)
HELIUS_summary_final <- HELIUS_summary_final %>% filter(Ferritin < 400)
```

# Filter for Age [>17]
```{r}
DIS_data_summary_final <- DIS_data_summary_final %>% filter(Age > 17)

PREV_summary_final <- PREV_summary_final %>%  filter(Age > 17)

NEW_data_summary_final <- NEW_data_summary_final %>% filter(Age > 17)

HELIUS_summary_final <- HELIUS_summary_final %>% filter(Age > 17)
```

# Filter Diabetes [Helius]
```{r}
HELIUS_summary_final <- HELIUS_summary_final %>% filter(Diabetes == "No")
```
# Filter on donation history DISIII
```{r}
DIS_data_summary_final <- DIS_data_summary_final %>% filter(!is.na(DaysToPreviousFB))
#DIS_data_summary_final <- DIS_data_summary_final %>% filter(DaysToPreviousFB < 1095)
# DIS_data_summary_final <- DIS_data_summary_final %>%
#   filter((Sex == "Men" & DaysToPreviousFB > 60) | Sex == "Women")
# DIS_data_summary_final <- DIS_data_summary_final %>%
#   filter((Sex == "Women" & DaysToPreviousFB > 122) | Sex == "Men")
# DIS_data_summary_final <- DIS_data_summary_final %>%
#   filter((Sex == "Men" & Donation_Freq_2YearsPrior < 11) | Sex == "Women")
# DIS_data_summary_final <- DIS_data_summary_final %>%
#   filter((Sex == "Women" & Donation_Freq_2YearsPrior < 7) | Sex == "Men")


```

## Final group N for the three cohorts
```{r}
# DIS
DIS_data_summary_final %>% 
   mutate(Group = dplyr::recode(Group, Pre_menopause_women = "Pre-menopausal women",
         Post_menopause_women = "Post-menopausal women")) %>% 
  group_by(Group) %>% 
  summarise ( N = n()) %>% 
  kable() 

# NEW
NEW_data_summary_final %>% 
   mutate(Group = dplyr::recode(Group, Pre_menopause_women = "Pre-menopausal women",
         Post_menopause_women = "Post-menopausal women")) %>% 
  group_by(Group) %>% 
  summarise ( N = n()) %>% 
  kable() 

# PREVEND
PREV_summary_final %>% 
   mutate(Group = dplyr::recode(Group, Pre_menopause_women = "Pre-menopausal women",
         Post_menopause_women = "Post-menopausal women")) %>% 
  group_by(Group) %>% 
  summarise ( N = n()) %>% 
  kable() 

# HELIUS
HELIUS_summary_final %>% 
   mutate(Group = dplyr::recode(Group, Pre_menopause_women = "Pre-menopausal women",
         Post_menopause_women = "Post-menopausal women")) %>% 
  group_by(Group) %>% 
  summarise ( N = n()) %>% 
  kable() 
```

## Select variables of interest for Cohort Dataset Merge
```{r}
# DIS
DIS_summary_final <- DIS_data_summary_final %>% 
  dplyr::select(ID, Group, Sex, Age,
                Ferritin, Hb, BMI, Menstruation, Smoking, blood_volume, DaysToPreviousFB, Weight, Group, Cohort, Donation_Freq_2YearsPrior, DaysToPreviousFB, Alcohol, Diet, TotalIron, HemeIron, NonHemeIron, CurrentOCC, CurrentOCCForContraception, CRP, Pregnancy, CurrentOCCForclimacterium, UlcurTreatment) 

# NEW
NEW_summary_final <- NEW_data_summary_final %>% 
  dplyr::select(ID, Group, Sex, Age,
                Ferritin, Hb, BMI, Menstruation, Smoking, blood_volume, DaysToPreviousFB, Weight, Group, Cohort, Donation_Freq_2YearsPrior, DaysToPreviousFB, Alcohol, Diet, TotalIron, HemeIron, NonHemeIron, CurrentOCC, CurrentOCCForContraception, CRP, Pregnancy,  UlcurTreatment) 

# PREV
PREV_summary_final <- PREV_summary_final %>% 
  dplyr::select(ID, Group, Sex, Age,
                Ferritin, Hb, BMI, Menstruation, Smoking, blood_volume, DaysToPreviousFB, Weight, Group, Cohort, Donation_Freq_2YearsPrior, DaysToPreviousFB, Alcohol, Diet, TotalIron, HemeIron, NonHemeIron, CurrentOCC, CurrentOCCForContraception, CRP, Pregnancy, UlcurTreatment) 


# HELIUS
HELIUS_summary_final <- HELIUS_summary_final %>% 
  dplyr::select(ID, Group, Sex, Age,
                Ferritin, Hb, BMI, Menstruation, Smoking, blood_volume, DaysToPreviousFB, Weight, Group, Cohort, Donation_Freq_2YearsPrior, DaysToPreviousFB, Alcohol, Diet, TotalIron, HemeIron, NonHemeIron, CurrentOCC, CurrentOCCForContraception, CRP, Pregnancy, UlcurTreatment)
```


# merge the cohorts and change Smoking 'missing'to N.A.
```{r}
summary_all_cohorts <- bind_rows(DIS_summary_final, NEW_summary_final, PREV_summary_final, HELIUS_summary_final)
```


## Final group N for the summarized table
```{r}
summary_all_cohorts %>% 
   mutate(Group = dplyr::recode(Group, Pre_menopause_women = "Pre-menopausal women",
         Post_menopause_women = "Post-menopausal women")) %>% 
  group_by(Group) %>% 
  summarise ( N = n()) %>% 
  kable() 

```

# Save Dataset
```{r}
saveRDS(summary_all_cohorts, file.path("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/", "1. Cohort Comparison - Merged Cohorts.rds"))
```






# Results - Regression table
## Rename and transform
```{r}
regression_cohorts <- summary_all_cohorts %>% 
    rename(donation_count = Donation_Freq_2YearsPrior,
            last_donation = DaysToPreviousFB,
            PreviousChildbirth = Pregnancy) %>% 
     mutate(Age = Age / 5, 
            donation_count_2 = donation_count^2,
            log_ferritin = log(Ferritin),
            log_last_donation = log(last_donation)/log(2),
            iron_deficiency = Ferritin < 15) 

regression_cohorts$Menstruation <- as.factor(regression_cohorts$Menstruation)
regression_cohorts$Smoking <- as.factor(regression_cohorts$Smoking)
regression_cohorts$Sex <- as.factor(regression_cohorts$Sex)
regression_cohorts$Group <- as.factor(regression_cohorts$Group)
regression_cohorts$Cohort <- as.factor(regression_cohorts$Cohort)
regression_cohorts$PreviousChildbirth <- as.character(regression_cohorts$PreviousChildbirth)
regression_cohorts$PreviousChildbirth[!(regression_cohorts$PreviousChildbirth %in% c("Yes", "No"))] <- NA  

# Remove ferritin of 0
regression_cohorts <- regression_cohorts %>% 
  group_by(Cohort) %>%
  filter(Ferritin > 0)

# Change contraception variable name
names(regression_cohorts)[names(regression_cohorts) == "CurrentOCC"] <- "Oral_contraception"

# Remove NES dataset
regression_cohorts <- regression_cohorts[!(regression_cohorts$Cohort == "NES"), ]

# Remove HELIUS dataset
regression_cohorts <- regression_cohorts[!(regression_cohorts$Cohort == "HELIUS"), ]

# Rename PREVEND 
regression_cohorts$Cohort <- gsub("PREVEND", "General Population", regression_cohorts$Cohort)

# Rename NEW
regression_cohorts$Cohort <- gsub("NEW", "New Donors", regression_cohorts$Cohort)
```

# Save Regression Data Dataset

```{r}
saveRDS(regression_cohorts, file.path("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/", "2. Cohort Comparison - Regression Data.rds"))
```



```{r}

```
