---
title: "5. Cohort Comparison - Tables & Plots"
author: "Jan Karregat"
date: "5-11-2023"
output: html_document
---


```{r setup, include=FALSE}
Sys.setlocale("LC_MESSAGES", 'en_GB.UTF-8')
Sys.setenv(LANG = "en_US.UTF-8")

knitr::opts_chunk$set(
        echo = FALSE,
        message = FALSE,
        warning = FALSE
)

currentDate <- format(Sys.time(), "%Y-%m-%d")
FolderName <- paste("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/3. R Plots/", currentDate,sep="")
dir.create(FolderName)


library(webshot)
library(patchwork)
library(lubridate)
library(plyr)
library(readr)
library(nFactors)
library(psych)
library(corrplot)
library(psych)
library(ggplot2)
library(ggthemes)
library(haven)
library(rsample)
library(broom)
library(scales)
library(kableExtra)
library(naniar)
library(haven)
library(foreign)
library(tableone)
library(stargazer)
library(gridExtra)
library(cowplot)
library(broom)
library(GGally)
library(ggfortify)
library(knitr)
library(lubridate)
library(car)
library(reshape2)
library(sfsmisc)
library(MASS)
library(ordinal)
library(sjmisc)
library(VIM)
library(epiDisplay)
library(epitools)
library(ez)
library(ggbeeswarm)
library(ggthemes)
library(rsample)
library(broom)
library(scales)
library(kableExtra)
library(boot)
library(readxl)
library(foreign)
library(corrr)
library(ggcorrplot)
library(tidyverse)
library(brms)
library(bayesplot)
library(tidylog, warn.conflicts = F)
```



# Table 1. - Open datasets

```{r}
# Dutch summary data
Table1_Dutch <- read.csv("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/3B. Cohort Comparison - Dutch Summary Data - Table 1.txt", header = TRUE, sep = "\t")

# Finnish summary data
Table1_Fin <- read.csv("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/3B. Cohort Comparison - Finnish Summary Data - Table 1.txt", header = TRUE, sep = "\t")

```


# Table 1. - Adjust names Dutch cohorts 

```{r}
# Raname variables
rename_list_Dutch <- list(
  "n" = "n",
  "age (mean (SD))" = "Age (mean (SD))",
  "blood_volume (mean (SD))" = "Blood volume (L) (mean (SD))",
  "ferritin (median [IQR])" = "Ferritin (ug/L) (median [IQR])",
  "Iron_Deficiency = TRUE (%)" = "Iron deficiency (%)",
  "Donation_Freq_2YearsPrior (mean (SD))" = "Number of donations in the last two years (median [IQR])",
  "DaysToPreviousFB (mean (SD))" = "Number of days since last donation (median [IQR])",
  "Smoking = Yes (%)" = "Smoking (%)",
  "Childbirth = Yes (%)" = "Childbirth in the past (median [IQR])",
  "Oral contraception = Yes (%)" = "Current oral contraception use (%)",
  "Menstruation = Yes (%)" = "Menstruation (%)"
)
rownames(Table1_Dutch) <- rename_list_Dutch[rownames(Table1_Dutch)]

# Change variable order
row_names_Dutch <- unlist(rename_list_Dutch)
Table1_Dutch <- Table1_Dutch[row_names_Dutch, ]

```


# Table 1. - Adjust names Finnish cohorts

```{r}
# Raname variables
rename_list_Fin <- list(
  "n" = "n",
  "Age (mean (SD))" = "Age (mean (SD))",
  "Blood volume (l) (mean (SD))" = "Blood volume (L) (mean (SD))",
  "Ferritin (ug/l) (median [IQR])" = "Ferritin (ug/L) (median [IQR])",
  "Iron deficiency = TRUE (%)" = "Iron deficiency (%)",
  "Donation frequency during past two years (median [IQR])" = "Number of donations in the last two years (median [IQR])",
  "Number of days since last whole blood donation (median [IQR])" = "Number of days since last donation (median [IQR])",
  "Smoking = yes (%)" = "Smoking (%)",
  "Childbirth in the past (median [IQR])" = "Childbirth in the past (median [IQR])",
  "Hormonal contraception = yes (%)" = "Current oral contraception use (%)",
  "Menstruation = Yes (%)" = "Menstruation (%)"
)
rownames(Table1_Fin) <- rename_list_Fin[rownames(Table1_Fin)]

# Change variable order
row_names_Fin <- unlist(rename_list_Fin)
Table1_Fin <- Table1_Fin[row_names_Fin, ]
```


# Table 1. - Combine Dutch & Finnish cohorts 

```{r}
# Bind Dutch and Finnish datasets
Table1_Combined <- cbind(Table1_Dutch, Table1_Fin)


# Create Group row
new_row_data <- setNames(data.frame(matrix(NA, ncol = ncol(Table1_Combined))), names(Table1_Combined))
Table1_Combined <- rbind(Table1_Combined, new_row_data)
rownames(Table1_Combined)[rownames(Table1_Combined) == "1"] <- "Group"

desired_order_parameter <- c("Group",
"n",
"Age (mean (SD))",
"Blood volume (L) (mean (SD))",
"Ferritin (ug/L) (median [IQR])",
"Iron deficiency (%)",
"Number of donations in the last two years (median [IQR])",
"Number of days since last donation (median [IQR])",
"Smoking (%)",
"Childbirth in the past (median [IQR])",
"Current oral contraception use (%)",
"Menstruation (%)")
Table1_Combined <- Table1_Combined[desired_order_parameter, ] 


```


# Table 1. - Formatting

```{r}
# Create Group row
identify_group <- function(colname) {
  if (grepl("(?i)\\bMen\\b", colname, ignore.case = TRUE)) {
    return("Men")
  } else if (grepl("Pre", colname, ignore.case = TRUE)) {
    return("Women \u226450 years")
  } else if (grepl("Post", colname, ignore.case = TRUE)) {
    return("Women >50 years")
  }
  return(NULL)
}

# Identify Group
for (col in colnames(Table1_Combined)) {
  group <- identify_group(col)
  if (!is.null(group)) {
    Table1_Combined["Group", col] <- group
  }
}

# Remove points in column names
colnames(Table1_Combined) <- gsub("\\.\\.", ".", colnames(Table1_Combined))

# Show values Group
unique(Table1_Combined["Group", ])


# Remove everything but the cohort name for columnnames
cohort_names <- sub("\\..*", "", colnames(Table1_Combined))

# Replace with column names
colnames(Table1_Combined) <- cohort_names
unique(colnames(Table1_Combined))

# Alter column order (Men, Premenopausal women, and Post menopausal women)
Table1_Combined <- Table1_Combined[,c(1:3,10,11,4:9,12:15)]
Table1_Combined <- Table1_Combined[,c(9:11,14,15,1:8,12,13)]

# Remove the 1 and 2 in the colnames
colnames(Table1_Combined) <- sub("\\.1$", "", colnames(Table1_Combined))
colnames(Table1_Combined) <- sub("\\.2$", "", colnames(Table1_Combined))
colnames(Table1_Combined)

```


# Table 1. - Produce and save

```{r}
Table1 <- kable(Table1_Combined) %>% kable_styling(latex_options = "striped")

kableTable <- kable(Table1_Combined) %>%
  kable_styling(latex_options = "striped", full_width = TRUE)

num_columns <- ncol(Table1_Combined)

# Pas de kolombreedte aan om wrappen te voorkomen voor elke kolom
for (i in 1:num_columns) {
  kableTable <- kableTable %>%
    column_spec(column = i, width = "10em", extra_css = "white-space: nowrap;")
}

webshot::install_phantomjs(force = TRUE)
kableExtra::save_kable(kableTable, "C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/5. Tables & figures/1. Table 1.png")
```


# Histogram - Ferritin 




# Prevalence plots - Open dataset sets

```{r}
# Dutch summary data
Prevalence_Dutch <-  readRDS("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/4A. Cohort Comparison - Dutch Summary Data - Prevalence plot.rds")

# Finnish summary data
Prevalence_Fin <- load(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/4B. Cohort Comparison - Finnish Summary Data - Prevalence Plot.rdata", verbose = TRUE)
Prevalence_Fin <- figure_data_FIN

# Combine datasets
Prevalence_Combined <- rbind(Prevalence_Dutch, Prevalence_Fin)

# change variable types to numeric
Prevalence_Combined$.lower <- as.numeric(Prevalence_Combined$.lower)
Prevalence_Combined$.estimate <- as.numeric(Prevalence_Combined$.estimate)
Prevalence_Combined$.upper <- as.numeric(Prevalence_Combined$.upper)
Prevalence_Combined$.alpha <- as.numeric(Prevalence_Combined$.alpha)
Prevalence_Combined$Country <- gsub("DUTCH", "Dutch", Prevalence_Combined$Country)
Prevalence_Combined$Country <- gsub("FIN", "Finnish", Prevalence_Combined$Country)
Prevalence_Combined$cohort  <- factor(Prevalence_Combined$cohort, levels = c("Blood donors", "General population", "New blood donors"))



```


# Prevalence plot - Create plot

```{r}
# Create ggplot
figure  <- ggplot(Prevalence_Combined, aes(x = term, y = .estimate, ymin = .lower, ymax = .upper, fill = cohort)) +
  scale_fill_manual(values=c("red", "blue", "green")) +
 geom_crossbar(alpha = 0.25, color = "dark gray", position = position_dodge(width = 0.6)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     breaks = seq(0,.8, by = 0.05)) +
  facet_grid(Country~sex) +
    theme_few() +
  xlab("Age") +
  ylab("Prevalence of iron deficiency") +
  theme(
    axis.text.y.left = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    axis.title.x = element_text(size = 16),
    axis.title.y.left = element_text(vjust = 1.5, size = 16),
    strip.text = element_text(size = 16),  
    strip.text.x = element_text(size = 16),
    legend.position = "bottom",
    legend.text = element_text(size = 16)  
  ) +
  guides(fill = guide_legend(ncol = 3))+
  labs(fill = "")

figure

# Save prevalence plot
FileName <- paste(FolderName, "/Prevalence plot.png",sep="")
ggsave(FileName, width = 15, height = 10)

```


# Linear regression - Datasets

```{r}
# Dutch summary data
Linear_Dutch <-  readRDS("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/5A. Cohort Comparison - Dutch Summary Data - Linear Regression.rds")
Linear_Dutch$Country <- "Dutch"
Linear_Dutch$Group <- gsub("Women premenopausal", "Women \u226450 years", Linear_Dutch$Group)
Linear_Dutch$Group <- gsub("Women postmenopausal", "Women >50 years", Linear_Dutch$Group)
Linear_Dutch$parameter <- gsub("New Donors", "New blood donor", Linear_Dutch$parameter)
Linear_Dutch$parameter <- gsub("General Population", "General population", Linear_Dutch$parameter)
Linear_Dutch$parameter <- gsub("log_last_donation", "Days since last blood donation (log transformed)", Linear_Dutch$parameter)
Linear_Dutch$parameter <- gsub("donation_count_2", "Number of blood donations (quadratic)", Linear_Dutch$parameter)
Linear_Dutch$parameter <- gsub("donation_count", "Number of blood donations", Linear_Dutch$parameter)
Linear_Dutch$parameter <- gsub("Childbirth", "Childbirth in the past", Linear_Dutch$parameter)
Linear_Dutch$parameter <- gsub("Oral contraception", "Hormonal contraception", Linear_Dutch$parameter)
Linear_Dutch$Model <- gsub("Model 1", "M1", Linear_Dutch$Model)
Linear_Dutch$Model <- gsub("Model 2", "M2", Linear_Dutch$Model)
Linear_Dutch$Model <- gsub("Model 3", "M3", Linear_Dutch$Model)
Linear_Dutch$Model <- gsub("Model 4", "M4", Linear_Dutch$Model)
Linear_Dutch$is.sig <- !(Linear_Dutch$ll <= 0 & 0 <= Linear_Dutch$hh)


# Finnish summary data
load(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/5B. Cohort Comparison - Finnish Summary Data - Linear Regression.rdata", verbose = TRUE)
Linear_Fin <- FinalForest_FIN
Linear_Fin$Country <- "Finnish"
Linear_Fin$Group <- gsub("Premenopausal Women", "Women \u226450 years", Linear_Fin$Group)
Linear_Fin$Group <- gsub("Postmenopausal Women", "Women >50 years", Linear_Fin$Group)
Linear_Fin$parameter <- gsub("General Population", "General population", Linear_Fin$parameter)
rows_to_change <- Linear_Fin$parameter == "Blood volume (Nadler)"
Linear_Fin$parameter[rows_to_change] <- "Blood volume"
Linear_Fin$Model <- gsub("Model 1", "M1", Linear_Fin$Model)
Linear_Fin$Model <- gsub("Model 2", "M2", Linear_Fin$Model)
Linear_Fin$Model <- gsub("Model 3", "M3", Linear_Fin$Model)
Linear_Fin$Model <- gsub("Model 4", "M4", Linear_Fin$Model)
Linear_Fin$is.sig <- !(Linear_Fin$ll <= 0 & 0 <= Linear_Fin$hh)



# Combine dataset
Linear_Combined <- rbind(Linear_Dutch, Linear_Fin)

# Save combined table
write.table(Linear_Combined, "C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/5. Tables & figures/Linear table I.txt", sep = "\t", quote = FALSE, col.names = TRUE, row.names = TRUE)
 
```


# Linear regression - Plots


```{r}
orlower_men <- -1
orupper_men <- 1

# Color definition 
color_mapping <- c(  "General population" = "#0000FF",  "New blood donor" = "#008000",  "Age" = "#FFA500",    "Blood volume" = "#FFA500",    "Number of blood donations" = "#FF0000",    "Number of blood donations (quadratic)" = "#FF0000",  
  "Days since last blood donation (log transformed)" = "#FF0000",    "Smoking" = "#800080",    "Childbirth in the past" = "#800080",   "Menstruation" = "#800080",  "Hormonal contraception" = "#800080")

# Dutch linear plot
desired_order_parameter <- c( "General population", "New blood donor", "Age", "Blood volume", "Number of blood donations", "Number of blood donations (quadratic)", "Days since last blood donation (log transformed)","Smoking", "Childbirth in the past", "Menstruation", "Hormonal contraception")
Linear_Dutch$parameter <- factor(Linear_Dutch$parameter, levels = rev(desired_order_parameter))

p_Dutch <- ggplot(Linear_Dutch, aes(x = m, y = parameter, color = parameter)) +
  geom_vline(xintercept = 0, color = "grey", linetype = "solid",
             size = 1)  +
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  xlim(orlower_men, orupper_men) +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
  guides(shape = "none") +
  labs(title = "Dutch") +
  xlab(" ") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")



# Finnish linear plot
desired_order_parameter_Fin <- c( "General population", "Age", "Blood volume",  "Number of blood donations", "Number of blood donations (quadratic)", "Days since last blood donation (log transformed)", "Smoking", "Childbirth in the past", "Menstruation", "Hormonal contraception")
Linear_Fin$parameter <- factor(Linear_Fin$parameter, levels = rev(desired_order_parameter_Fin))

p_Fin <- ggplot(Linear_Fin, aes(x = m, y = parameter, color = parameter))  +
  geom_vline(xintercept = 0, color = "grey", linetype = "solid",
             size = 1) +
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  xlim(orlower_men, orupper_men)  +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
  guides(shape = "none") +
  labs(title = "Finnish") +
  xlab("Coefficient") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")



# Combined linear plot
dutch_plot <- p_Dutch + theme(strip.text.x = element_text(size = 14))
finnish_plot <- p_Fin +  theme(strip.text.x = element_blank())

final_plot <-  dutch_plot/finnish_plot

final_plot

FileName <- paste(FolderName, "/Forest Plot - Linear Final - Combined.png",sep="")
ggsave(FileName, width = 15, height = 10)
```

# Logistic regression - Datasets

```{r}
# Dutch summary data
Logistic_Dutch <-  readRDS("C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/6A. Cohort Comparison - Dutch Summary Data - Logistic Regression.rds")
Logistic_Dutch$Country <- "Dutch"
Logistic_Dutch$Group <- gsub("Women Premenopausal", "Women \u226450 years", Logistic_Dutch$Group)
Logistic_Dutch$Group <- gsub("Women Postmenopausal", "Women >50 years", Logistic_Dutch$Group)
Logistic_Dutch$parameter <- gsub("New Donors", "New blood donor", Logistic_Dutch$parameter)
Logistic_Dutch$parameter <- gsub("General Population", "General population", Logistic_Dutch$parameter)
Logistic_Dutch$parameter <- gsub("log_last_donation", "Days since last blood donation (log transformed)", Logistic_Dutch$parameter)
Logistic_Dutch$parameter <- gsub("donation_count_2", "Number of blood donations (quadratic)", Logistic_Dutch$parameter)
Logistic_Dutch$parameter <- gsub("donation_count", "Number of blood donations", Logistic_Dutch$parameter)
Logistic_Dutch$parameter <- gsub("Childbirth", "Childbirth in the past", Logistic_Dutch$parameter)
Logistic_Dutch$parameter <- gsub("Oral contraception", "Hormonal contraception", Logistic_Dutch$parameter)
Logistic_Dutch$Model <- gsub("Model 1", "M1", Logistic_Dutch$Model)
Logistic_Dutch$Model <- gsub("Model 2", "M2", Logistic_Dutch$Model)
Logistic_Dutch$Model <- gsub("Model 3", "M3", Logistic_Dutch$Model)
Logistic_Dutch$Model <- gsub("Model 4", "M4", Logistic_Dutch$Model)
Logistic_Dutch$is.sig <- !(Logistic_Dutch$ll <= 1 & 1 <= Logistic_Dutch$hh)

# Finnish summary data
load(file="C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/2. R Datasets/6B. Cohort Comparison - Finnish Summary Data - Logistic Regression.rdata", verbose = TRUE)
Logistic_Fin <- FinalForest_FIN_log
Logistic_Fin$Country <- "Finnish"
Logistic_Fin$Group <- gsub("Premenopausal Women", "Women \u226450 years", Logistic_Fin$Group)
Logistic_Fin$Group <- gsub("Postmenopausal Women", "Women >50 years", Logistic_Fin$Group)
Logistic_Fin$parameter <- gsub("General Population", "General population", Logistic_Fin$parameter)
rows_to_change <- Logistic_Fin$parameter == "Blood volume (Nadler)"
Logistic_Fin$parameter[rows_to_change] <- "Blood volume"
Logistic_Fin$Model <- gsub("Model 1", "M1", Logistic_Fin$Model)
Logistic_Fin$Model <- gsub("Model 2", "M2", Logistic_Fin$Model)
Logistic_Fin$Model <- gsub("Model 3", "M3", Logistic_Fin$Model)
Logistic_Fin$Model <- gsub("Model 4", "M4", Logistic_Fin$Model)
Logistic_Fin$is.sig <- !(Logistic_Fin$ll <= 1 & 1 <= Logistic_Fin$hh)

# Combine dataset
Logistic_Combined <- rbind(Logistic_Dutch, Logistic_Fin)

# Save combined table
 write.table(Logistic_Combined, "C:/Users/karre01j/OneDrive - Sanquin/A FORTE/A3 Collaboration Finland/1. Cohort Comparison Analysis/2. Analysis [R]/5. Tables & figures/Logistic table.txt", sep = "\t", quote = TRUE, col.names = TRUE, row.names = TRUE)
```


# Logistic regression - Plots

```{r}
# Color definition 
color_mapping <- c(  "General population" = "#0000FF",  "New blood donor" = "#008000",  "Age" = "#FFA500",    "Blood volume" = "#FFA500",    "Number of blood donations" = "#FF0000",    "Number of blood donations (quadratic)" = "#FF0000",  
  "Days since last blood donation (log transformed)" = "#FF0000",    "Smoking" = "#800080",    "Childbirth in the past" = "#800080",   "Menstruation" = "#800080",  "Hormonal contraception" = "#800080")

# Adjust CI limit to fit plot
  Hist_Log_Dutch <- Logistic_Dutch %>% mutate(
    hh = (ifelse(hh>100,100,hh))
  )

# Dutch logistic plot
desired_order_parameter <- c( "General population", "New blood donor", "Age", "Blood volume", "Number of blood donations", "Number of blood donations (quadratic)", "Days since last blood donation (log transformed)","Smoking", "Childbirth in the past", "Menstruation", "Hormonal contraception")
Hist_Log_Dutch$parameter <- factor(Hist_Log_Dutch$parameter, levels = rev(desired_order_parameter))

p_Dutch <- ggplot(Hist_Log_Dutch, aes(x = m, y = parameter, color = parameter)) +
  geom_vline(xintercept = 1, color = "grey", linetype = "solid",
             size = 1)  +
  scale_x_log10(
    limits = c(0.01, 100),
    labels = function(x) {
      ifelse(x %in% c(1, 10, 100), as.character(x), label_number()(x))
    }
    )+
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
  guides(shape = "none") +
  labs(title = "Dutch") +
  xlab(" ") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")

p_Dutch

FileName <- paste(FolderName, "/FinalForest_Log_Dutch.png",sep="")
ggsave(FileName, width = 15, height = 10)


# Finnish logistic plot
# Adjust CI limit to fit plot
  Hist_Log_Fin <- Logistic_Fin %>% mutate(
    hh = (ifelse(hh>100,100,hh))
  )
  
# Adjust color scheme
desired_order_parameter_Fin <- c("General population", "Age", "Blood volume",  "Number of blood donations", "Number of blood donations (quadratic)", "Days since last blood donation (log transformed)", "Smoking", "Childbirth in the past", "Menstruation", "Hormonal contraception")
Hist_Log_Fin$parameter <- factor(Hist_Log_Fin$parameter, levels = rev(desired_order_parameter_Fin))


p_Fin <- ggplot(Hist_Log_Fin, aes(x = m, y = parameter, color = parameter)) +
  geom_vline(xintercept = 1, color = "grey", linetype = "solid",
             size = 1) +
  scale_x_log10(
    limits = c(0.01, 100),
    labels = function(x) {
      ifelse(x %in% c(1, 10, 100), as.character(x), label_number()(x))
    }
    )+
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
  guides(shape = "none") +
  labs(title = "Finnish") +
  xlab("OR") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")

p_Fin

FileName <- paste(FolderName, "/FinalForest_Log_Fin.png",sep="")
ggsave(FileName, width = 15, height = 10)



# Create separate plot objects
dutch_plot <- p_Dutch + theme(strip.text.x = element_text(size = 14))
finnish_plot <- p_Fin +  theme(strip.text.x = element_blank())


# Combine plots
final_plot <-  dutch_plot / finnish_plot
final_plot

FileName <- paste(FolderName, "/FinalForest_Log_Combined.png",sep="")
ggsave(FileName, width = 15, height = 10)



```











# Linear regression - Plots - Cohort effects only


```{r}
Linear_Dutch_Cohort <- Linear_Dutch[c(1,2,5,6,12,13,20:22,25,26,32,33,40,44,45,48,49,55,56,63),]

orlower_men <- -1
orupper_men <- 1

# Color definition 
color_mapping <- c(  "General population" = "#0000FF",  "New blood donor" = "#008000")

# Dutch linear plot
desired_order_parameter <- c( "General population", "New blood donor")
Linear_Dutch_Cohort$parameter <- factor(Linear_Dutch_Cohort$parameter, levels = rev(desired_order_parameter))

p_Dutch_Cohort <- ggplot(Linear_Dutch_Cohort, aes(x = m, y = parameter, color = parameter)) +
  geom_vline(xintercept = 0, color = "grey", linetype = "solid",
             size = 1)  +
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  #scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  xlim(orlower_men, orupper_men) +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "bottom"
  ) +
  guides(color = guide_legend(title = NULL), shape = "none")  +
  labs(title = "Dutch") +
  xlab(" ") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")
p_Dutch_Cohort


# Finnish linear plot
Linear_Fin_Cohort <- Linear_Fin[c(1,4,10,17:19,22,34,38,41,47,54),]

desired_order_parameter_Fin <- c( "General population")
Linear_Fin_Cohort$parameter <- factor(Linear_Fin_Cohort$parameter, levels = rev(desired_order_parameter_Fin))

p_Fin_Cohort <- ggplot(Linear_Fin_Cohort, aes(x = m, y = parameter, color = parameter))  +
  geom_vline(xintercept = 0, color = "grey", linetype = "solid",
             size = 1) +
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  xlim(orlower_men, orupper_men)  +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
  guides(shape = "none") +
  labs(title = "Finnish") +
  xlab("Coefficient") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")
p_Fin_Cohort


# Combined linear plot
dutch_plot_Cohort <- p_Dutch_Cohort + theme(strip.text.x = element_text(size = 14))
finnish_plot_Cohort <- p_Fin_Cohort +  theme(strip.text.x = element_blank())

final_plot_Cohort <-  dutch_plot_Cohort/finnish_plot_Cohort

final_plot_Cohort

FileName <- paste(FolderName, "/Forest Plot - Linear Final - Cohorts only.png",sep="")
ggsave(FileName, width = 15, height = 10)



```


# Logistic regression - Plots - Cohort only

```{r}
# Color definition 
color_mapping <- c(  "General population" = "#0000FF",  "New blood donor" = "#008000")

# Select only cohort effect sizes an adjust CI limit to fit plot
Hist_Log_Dutch_Cohort <- Hist_Log_Dutch[c(1,2,5,6,12,13,20:22,25,26,27,33,40,44,45,48,49,55,56,63),]
  Hist_Log_Dutch_Cohort <- Hist_Log_Dutch_Cohort %>% mutate(
    hh = (ifelse(hh>100,100,hh))
  )

# Dutch logistic plot
desired_order_parameter <- c( "General population", "New blood donor")
Hist_Log_Dutch_Cohort$parameter <- factor(Hist_Log_Dutch_Cohort$parameter, levels = rev(desired_order_parameter))

p_Dutch_Cohort_Log <- ggplot(Hist_Log_Dutch_Cohort, aes(x = m, y = parameter, color = parameter)) +
  geom_vline(xintercept = 1, color = "grey", linetype = "solid",
             size = 1)  +
  scale_x_log10(
    limits = c(0.001, 100),
    labels = function(x) {
      ifelse(x %in% c(1, 10, 100), as.character(x), label_number()(x))
    }
    )+
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "bottom"
  ) +
  guides(color = guide_legend(title = NULL), shape = "none") +
  labs(title = "Dutch") +
  xlab(" ") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")

p_Dutch_Cohort_Log

FileName <- paste(FolderName, "/FinalForest_Log_Dutch_Cohorts.png",sep="")
ggsave(FileName, width = 15, height = 10)


# Finnish logistic plot
Hist_Log_Fin_Cohort <- Hist_Log_Fin[c(1,4,10,17:18,21,27,34,38,41,47,54),]
# Adjust CI limit to fit plot
  Hist_Log_Fin_Cohort <- Hist_Log_Fin_Cohort %>% mutate(
    hh = (ifelse(hh>100,100,hh))
  )
  
esired_order_parameter_Fin <- c( "Men", "Women Premenopausal", "Women Postmenopausal")
Hist_Log_Fin_Cohort$Group <- factor(Hist_Log_Fin_Cohort$Group, levels = esired_order_parameter_Fin)
  
# Adjust color scheme
#desired_order_parameter_Fin <- c("General population", "Age", "Blood volume",  "Number of blood donations", "Number of blood donations (quadratic)", "Days since last blood donation (log transformed)", "Smoking", "Childbirth in the past", "Menstruation", "Hormonal contraception")
#Hist_Log_Fin_Cohort$parameter <- factor(Hist_Log_Fin_Cohort$parameter, levels = rev(desired_order_parameter_Fin))


p_Fin_Cohort_Log <- ggplot(Hist_Log_Fin_Cohort, aes(x = m, y = parameter, color = parameter)) +
  geom_vline(xintercept = 1, color = "grey", linetype = "solid",
             size = 1) +
  scale_x_log10(
    limits = c(0.001, 100),
    labels = function(x) {
      ifelse(x %in% c(1, 10, 100), as.character(x), label_number()(x))
    }
    )+
  geom_point(aes(shape = is.sig), size = 4) +
  geom_linerange(aes(xmin = ll, xmax = hh),
                 size = 1,
                 linetype = 1
  ) +
  scale_shape_manual(values = c(1, 16)) +
  scale_color_manual(values = c(color_mapping)) +
  theme_gray() +
  theme(
    axis.title = element_text(size = 14),
    strip.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.background = element_rect(fill = "white"),
    strip.background.x = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_line(color = "gray", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
  ) +
  guides(shape = "none") +
  labs(title = "Finnish") +
  xlab("OR") +
  ylab(" ") +
  facet_grid(Model ~ Group, scale = "free_y", space = "free_y")

p_Fin_Cohort_Log

FileName <- paste(FolderName, "/FinalForest_Log_Finh_Cohorts.png",sep="")
ggsave(FileName, width = 15, height = 10)



# Create separate plot objects
dutch_plot_Cohort_Log <- p_Dutch_Cohort_Log + theme(strip.text.x = element_text(size = 14))
finnish_plot_Cohort_Log <- p_Fin_Cohort_Log +  theme(strip.text.x = element_blank())


# Combine plots
final_plot_Cohorts <-  dutch_plot_Cohort_Log / finnish_plot_Cohort_Log
final_plot_Cohorts

FileName <- paste(FolderName, "/FinalForest_Log_Combined_Cohorts.png",sep="")
ggsave(FileName, width = 15, height = 10)
```
